Reviewer comments from PeerJ

### 2015-02-20 PeerJResponse.tex
Edits to response
Edits to response, reviewer 1

>>>>

\res{Data were previously phased using fastPHASE (\lef{cite tanja and fastPHASE paper}). We have added clarifying statements to the text of this section, pages X, lines X-X. Figure 4 is showing maize population assignment for adjacent 5 kb windows. The STRUCTURE analysis was performed for the entirety of chromosome 1; however, the figure only shows a zoomed in portion to highlight the section of chromosome 1 that contains the \emph{tb1} region. The results in Table 4 reflect the entire chromosome.}
